\textbf{Causal graph quantum dynamic simulation}

### 2021-06-02 paper/paper.tex
deleted older version and continued optimizing

\begin{lstlisting}[style=CStyle]
	//...
	void step_split_merge_all(bool step, bool split_merge, bool reversed) {
		graph_map_t buff;
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
	  	for (auto & [graph, mag] : buff)
		#pragma omp task
	  	{
	  		if (step)
	  			graph->step();

	  		if (reversed)
	  			graph->reversed_step();

	  		if (split_merge) {
	  			auto split_merge = get_split_merge(graph);

@@

				  	//add graph
				  	graphs_.insert({g_, mag * mag_split_merge});
				}
				// update the probability of the graph without split or merge 
				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
				mag *= mag_no_split_merge;
	  		}

	  		//add graph
			graphs_.insert({graph, mag});
	  	}
	}
	//...
\end{lstlisting}

>>>>

\begin{lstlisting}[style=CStyle]
	//...
	void step_split_merge_all() {
		graph_map_t buff;
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
		for (auto & [graph, mag] : buff)
		#pragma omp task
	  	{

	  		graph->step(); //graph->reversed_step(); for reversed_split_merge_step_all()

	  		auto split_merge = get_split_merge(graph);

	  		#pragma omp task
	  		{
	  			// update the probability of the graph without split or merge 
				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
				graphs_.insert({graph, mag * mag_no_split_merge});
	  		}

@@

	  			//add graph
	  			graphs_.insert({g_, mag * mag_split_merge});
	  		}
	  	}
	}
	//...
\end{lstlisting}
